---
title: 'univariate analysis: UB55'
author: "michael freund"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    highlight: zenburn
---

# intro



```{r setup, include = FALSE}

knitr::opts_chunk$set(
  cache = TRUE, echo = FALSE, warning = FALSE, message = FALSE,
  fig.align = 'center',
  fig.width = 11.5, fig.fullwidth = TRUE
)

set.seed(0)

source(here("code", "_packages"))
source(here("code", "read-behav.R"))
source(here("code", "_vars.R"))

## settings ----

theme_set(theme_light(base_size = 10))
glminfo <- data.frame(
  task = c("Axcpt", "Cuedts", "Stern", "Stroop"),
  name.glm = c(
    "baseline_Cues_EVENTS_censored_shifted", 
    "baseline_CongruencySwitch_EVENTS_censored_shifted",
    "baseline_ListLength_EVENTS_censored_shifted",
    "baseline_Congruency_EVENTS_censored_shifted"
  )
)
glminfo <- as.data.table(glminfo)


## data ----

d <- setNames(vector("list", nrow(glminfo)), glminfo$task)
for (glm.i in seq_len(nrow(glminfo))) {
  
  a <- readRDS(here("out", "glms", paste0("roistats_", glminfo[glm.i]$task, "_", glminfo[glm.i]$name.glm, ".RDS")))
  a <- as.data.table(reshape2::melt(a))
  
  a <- separate(a, term, c("term", "stat"), "_")
  a <- a[!grepl("Full|block", term) & stat != "Fstat"]
  a <- separate(a, term, c("term", "tr"), "#")
  
  a$network <- a$parcel %>% gsub("^Mean_7Networks_LH_", "", .) %>% gsub("_.*", "", .)
  
  a <- dcast(a, term + tr + parcel + subj + run + hemi ~ stat, value.var = "value")
  names(a) <- tolower(names(a))
  
  d[[glm.i]] <- a
  
}
rm(glm.i, a)



```


# Estimated marginal HRFs

## By network

* Curves plot mean betas at each knot.
* Betas averaged across conditions (biasCon, ..., PC50InCon) by parcel, then by network, within subject.
* Bands represent 95% CIs across subjects.
* betas from two GLMs presented: **green** is 1tr1knot, **orange** is 2tr1knot


```{r hrfs_by_network, fig.height = 7, fig.width = 11}

means.d %>%
  
  group_by(run, session, glm, network, tr, subj) %>%
  summarize(m = mean(m))  %>% ## average across conditions and parcels
  
  ggplot(aes(tr, m, fill = glm)) +
  geom_hline(yintercept = 0) +
  stat_summary(fun.data = "mean_cl_boot", geom = "ribbon", alpha = 0.75) +
  
  facet_grid(vars(network), vars(session, run)) +
  scale_fill_brewer(type = "qual", palette = 2) +
  theme(legend.position = "none")

```


## By parcel

* Betas averaged across conditions (biasCon, ..., PC50InCon) and subjects, within parcel.


```{r hrfs_by_parcel, fig.height = 7, fig.width = 11}

grid.arrange(
  
  means.d %>%
    
    filter(glm == "2tr1knot") %>%
    
    group_by(run, session, network, tr, parcel, glm) %>%
    summarize(m = mean(m))  %>% ## average across subjects
    
    ggplot(aes(tr, m, group = parcel, color = glm)) +
    geom_hline(yintercept = 0) +
    stat_summary(fun.y = "mean", geom = "line", size = 1, alpha = 0.5) +
    
    facet_grid(vars(network), vars(session, run)) +
    scale_color_manual(values = colors.glm) +
    scale_y_continuous(limits = c(-0.75, 3)) +
    scale_x_continuous(limits = c(0, 12), breaks = seq(0, 12, 4)) +
    theme(legend.position = "none") +
    labs(title = "2tr1knot", y = "mean beta"),
  
  means.d %>%
    
    filter(glm == "1tr1knot") %>%
    
    group_by(run, session, network, tr, parcel, glm) %>%
    summarize(m = mean(m))  %>% ## average across subjects
    
    ggplot(aes(tr, m, group = parcel, color = glm)) +
    geom_hline(yintercept = 0) +
    stat_summary(fun.y = "mean", geom = "line", size = 1, alpha = 0.5) +
    
    facet_grid(vars(network), vars(session, run)) +
    scale_color_manual(values = colors.glm) +
    scale_y_continuous(limits = c(-0.75, 3)) +
    scale_x_continuous(limits = c(0, 12), breaks = seq(0, 12, 4)) +
    theme(legend.position = "none") +
    labs(title = "1tr1knot", y = "mean beta"),
  
  ncol = 2
  
)

```

## DMCC 30

# Contrasts

```{r contrasts_stats}

## main effects models ----

stats.trial.type <- means.d %>%
  
  group_by(tr, parcel, session, network, glm, subj, trial.type) %>%  ## average across runs, PC
  summarize(m = mean(m)) %>% 
  
  group_by(tr, parcel, session, network, glm) %>%  ## get t values
  tidyr::pivot_wider(names_from = trial.type, values_from = m) %>%
  summarize(
    statistic = t.test(InCon, Con, paired = TRUE)$statistic,
    p.value   = t.test(InCon, Con, paired = TRUE)$p.value
  ) %>%
  
  group_by(tr, session, glm) %>%  ## adjust
  mutate(p.fdr = p.adjust(p.value, "fdr"))

stats.pc <- means.d %>%
  
  group_by(tr, parcel, session, network, glm, subj, pc) %>%  ## average across runs, trial.type
  summarize(m = mean(m)) %>% 
  
  group_by(tr, parcel, session, network, glm) %>%  ## get t values
  tidyr::pivot_wider(names_from = pc, values_from = m) %>%
  summarize(
    statistic = t.test(bias, PC50, paired = TRUE)$statistic,
    p.value   = t.test(bias, PC50, paired = TRUE)$p.value
  ) %>%
  
  group_by(tr, session, glm) %>%  ## adjust
  mutate(p.fdr = p.adjust(p.value, "fdr"))

stats.run <- means.d %>%
  
  group_by(tr, parcel, session, network, glm, subj, run) %>%  ## average across trial.type, PC
  summarize(m = mean(m)) %>% 
  
  group_by(tr, parcel, session, network, glm) %>%  ## get t values
  tidyr::pivot_wider(names_from = run, values_from = m) %>%
  summarize(
    statistic = t.test(run1, run2, paired = TRUE)$statistic,
    p.value   = t.test(run1, run2, paired = TRUE)$p.value
  ) %>%
  
  group_by(tr, session, glm) %>%  ## adjust
  mutate(p.fdr = p.adjust(p.value, "fdr"))

```

## Main effects: run, pc, trialtype

* A linear model was fit on each parcel\*session\*knot, with dummy-coded regresssors for **run**, **proportion congruence**, (pc50, bias) and **trial type** (congruent, incongruent).

* random intercept by subject.

* Points plot parcel-wise t statistic for each parcel. Those filled in are significant after whole-brain FDR correction.

```{r contrasts_by_parcel, fig.height = 7, fig.width = 11}

## run

stats.run %>%
  
  filter(glm == "2tr1knot") %>%

  ggplot(aes(tr, statistic)) +
  geom_beeswarm(
    aes(fill = network, alpha = p.fdr < 0.05, color = ifelse(p.fdr < 0.05, "black", "white")),
    size = 1.5, shape = 21
  ) +
  
  scale_color_identity() +
  scale_alpha_manual(values = c("TRUE" = 1, "FALSE" = 0.2)) +
  facet_grid(vars(network), vars(session)) +
  geom_hline(yintercept = 0) +
  scale_fill_brewer(type = "qual", palette = 1) +
  scale_x_continuous(limits = c(0, 13), breaks = seq(0, 12)) +
  
  theme(legend.position = "none") +
  labs(title = "run (run1 - run2): 2tr1knot", x = "TR (post stimulus onset)", y = "t statistic")
  
stats.run %>%
  
  filter(glm == "1tr1knot") %>%

  ggplot(aes(tr, statistic)) +
  geom_beeswarm(
    aes(fill = network, alpha = p.fdr < 0.05, color = ifelse(p.fdr < 0.05, "black", "white")),
    size = 1.5, shape = 21
  ) +
  
  scale_color_identity() +
  scale_alpha_manual(values = c("TRUE" = 1, "FALSE" = 0.2)) +
  facet_grid(vars(network), vars(session)) +
  geom_hline(yintercept = 0) +
  scale_fill_brewer(type = "qual", palette = 1) +
  scale_x_continuous(limits = c(0, 13), breaks = seq(0, 12)) +
  
  theme(legend.position = "none") +
  labs(title = "run (run1 - run2): 1tr1knot", x = "TR (post stimulus onset)", y = "t statistic")



## pc

stats.pc %>%
  
  filter(glm == "2tr1knot") %>%

  ggplot(aes(tr, statistic)) +
  geom_beeswarm(
    aes(fill = network, alpha = p.fdr < 0.05, color = ifelse(p.fdr < 0.05, "black", "white")),
    size = 1.5, shape = 21
  ) +
  
  scale_color_identity() +
  scale_alpha_manual(values = c("TRUE" = 1, "FALSE" = 0.2)) +
  facet_grid(vars(network), vars(session)) +
  geom_hline(yintercept = 0) +
  scale_fill_brewer(type = "qual", palette = 1) +
  scale_x_continuous(limits = c(0, 13), breaks = seq(0, 12)) +
  
  theme(legend.position = "none") +
  labs(title = "pc (bias - PC50): 2tr1knot", x = "TR (post stimulus onset)", y = "t statistic")
  
stats.pc %>%
  
  filter(glm == "1tr1knot") %>%

  ggplot(aes(tr, statistic)) +
  geom_beeswarm(
    aes(fill = network, alpha = p.fdr < 0.05, color = ifelse(p.fdr < 0.05, "black", "white")),
    size = 1.5, shape = 21
  ) +
  
  scale_color_identity() +
  scale_alpha_manual(values = c("TRUE" = 1, "FALSE" = 0.2)) +
  facet_grid(vars(network), vars(session)) +
  geom_hline(yintercept = 0) +
  scale_fill_brewer(type = "qual", palette = 1) +
  scale_x_continuous(limits = c(0, 13), breaks = seq(0, 12)) +
  
  theme(legend.position = "none") +
  labs(title = "pc (bias - PC50): 1tr1knot", x = "TR (post stimulus onset)", y = "t statistic")


## stroop

stats.trial.type %>%
  
  filter(glm == "2tr1knot") %>%

  ggplot(aes(tr, statistic)) +
  geom_beeswarm(
    aes(fill = network, alpha = p.fdr < 0.05, color = ifelse(p.fdr < 0.05, "black", "white")),
    size = 1.5, shape = 21
  ) +
  
  scale_color_identity() +
  scale_alpha_manual(values = c("TRUE" = 1, "FALSE" = 0.2)) +
  facet_grid(vars(network), vars(session)) +
  geom_hline(yintercept = 0) +
  scale_fill_brewer(type = "qual", palette = 1) +
  scale_x_continuous(limits = c(0, 13), breaks = seq(0, 12)) +
  
  theme(legend.position = "none") +
  labs(title = "stroop: 2tr1knot", x = "TR (post stimulus onset)", y = "t statistic")
  
stats.trial.type %>%
  
  filter(glm == "1tr1knot") %>%

  ggplot(aes(tr, statistic)) +
  geom_beeswarm(
    aes(fill = network, alpha = p.fdr < 0.05, color = ifelse(p.fdr < 0.05, "black", "white")),
    size = 1.5, shape = 21
  ) +
  
  scale_color_identity() +
  scale_alpha_manual(values = c("TRUE" = 1, "FALSE" = 0.2)) +
  facet_grid(vars(network), vars(session)) +
  geom_hline(yintercept = 0) +
  scale_fill_brewer(type = "qual", palette = 1) +
  scale_x_continuous(limits = c(0, 13), breaks = seq(0, 12)) +
  
  theme(legend.position = "none") +
  labs(title = "stroop: 1tr1knot", x = "TR (post stimulus onset)", y = "t statistic")

```

## Interaction: PC\*stroop

* Is the stroop effect larger for bias items than PC50 in baseline?

* Opposite true in proactive?

* No parcels were significant after FDR correction. "Filled in" points have p < 0.05, uncorrected.

```{r interaction_pc_stroop, fig.height = 7, fig.width = 11}

## fit

means.l.x <- means.d %>% split(paste(.$tr, .$parcel, .$session, .$network, .$glm, sep = "."))
means.l.x <- lapply(means.l.x, function(x) lmer(m ~ run + pc * trial.type + (1 | subj), x))

## extract

tidy_lmer <- function(x) {
  coefs <- as.data.frame(coef(summary(x)))
  coefs$term <- rownames(coefs)
  dplyr::rename(coefs, estimate = "Estimate", se = "Std. Error", "statistic" = "t value", p.value = "Pr(>|t|)")
}

coef.means.x <- lapply(means.l.x, tidy_lmer)

## format

coef.means.x %<>%
  bind_rows(.id = "model.id") %>%
  cbind(reshape2::colsplit(.$model.id, "\\.", c("tr", "parcel", "session", "network", "glm")))

## adjust

coef.means.x %<>%  
  group_by(tr, session, glm) %>%
  mutate(p.fdr = p.adjust(p.value, "fdr"))

## plot

coef.means.x %>%
  
  filter(glm == "2tr1knot", term == "pcbias:trial.typeInCon") %>%

  ggplot(aes(tr, statistic)) +
  geom_beeswarm(
    aes(fill = network, alpha = p.value < 0.05, color = ifelse(p.value < 0.05, "black", "white")),
    size = 1.5, shape = 21
  ) +
  
  scale_color_identity() +
  scale_alpha_manual(values = c("TRUE" = 1, "FALSE" = 0.2)) +
  facet_grid(vars(network), vars(session)) +
  geom_hline(yintercept = 0) +
  scale_fill_brewer(type = "qual", palette = 1) +
  scale_x_continuous(limits = c(0, 13), breaks = seq(0, 12)) +
  
  theme(legend.position = "none") +
  labs(title = "stroop*trial.type: 2tr1knot", x = "TR (post stimulus onset)", y = "t statistic")


coef.means.x %>%
  
  filter(glm == "1tr1knot", term == "pcbias:trial.typeInCon") %>%

  ggplot(aes(tr, statistic)) +
  geom_beeswarm(
    aes(fill = network, alpha = p.value < 0.05, color = ifelse(p.value < 0.05, "black", "white")),
    size = 1.5, shape = 21
  ) +
  
  scale_color_identity() +
  scale_alpha_manual(values = c("TRUE" = 1, "FALSE" = 0.2)) +
  facet_grid(vars(network), vars(session)) +
  geom_hline(yintercept = 0) +
  scale_fill_brewer(type = "qual", palette = 1) +
  scale_x_continuous(limits = c(0, 13), breaks = seq(0, 12)) +
  
  theme(legend.position = "none") +
  labs(title = "stroop*trial.type: 1tr1knot", x = "TR (post stimulus onset)", y = "t statistic")


```


## Defining ROIs

* looks like the action is in TRs 2--6.

* Here a single model is fit to all data across this epoch.

* t statistics from 2tr1knot and 1tr1knot models are plotted against each other.

```{r, fig.height = 15, fig.width = 8}

## fit

means.l.roi <- means.d %>% filter(tr > 1, tr < 7) %>% split(paste(.$parcel, .$session, .$network, .$glm, sep = "."))
means.l.roi <- lapply(means.l.roi, function(x) lmer(m ~ run + pc + trial.type + (1 | subj), x))

## extract

coef.means.roi <- lapply(means.l.roi, tidy_lmer)

## format

coef.means.roi %<>%
  bind_rows(.id = "model.id") %>%
  cbind(reshape2::colsplit(.$model.id, "\\.", c("parcel", "session", "network", "glm")))

## adjust

coef.means.roi %<>%  
  group_by(session, glm) %>%
  mutate(p.fdr = p.adjust(p.value, "fdr"))

## plot

coef.means.roi %>%
  
  filter(term == "trial.typeInCon") %>%
  select(-p.value, -p.fdr, -estimate, -se, -df, -model.id) %>%
  tidyr::pivot_wider(names_from = "glm", values_from = statistic, names_prefix = "glm.") %>%
  
  ggplot(aes(glm.1tr1knot, glm.2tr1knot)) +
  geom_point(
    aes(),
    size = 1.5, shape = 21, fill = "black", color = "grey"
  ) +
  
  facet_grid(vars(network), vars(session)) +
  geom_hline(yintercept = 0) +
  geom_vline(xintercept = 0) +
  geom_abline() +
  
  labs(title = "stroop t statistics, estimated over TRs 2-6")

```


```{r}

roi.univ.bas.1tr1knot <- coef.means.roi %>%
  filter(
    p.fdr < 0.05, session == "baseline", statistic > 0, term == "trial.typeInCon",
    glm == "1tr1knot"
    ) %>%
  pull(parcel) %>%
  unique

roi.univ.bas.2tr1knot <- coef.means.roi %>%
  filter(
    p.fdr < 0.05, session == "baseline", statistic > 0, term == "trial.typeInCon",
    glm == "2tr1knot"
    ) %>%
  pull(parcel) %>%
  unique

roi.univ.pro.1tr1knot <- coef.means.roi %>%
  filter(
    p.fdr < 0.05, session == "proactive", statistic > 0, term == "trial.typeInCon",
    glm == "1tr1knot"
    ) %>%
  pull(parcel) %>%
  unique

roi.univ.pro.2tr1knot <- coef.means.roi %>%
  filter(
    p.fdr < 0.05, session == "proactive", statistic > 0, term == "trial.typeInCon",
    glm == "2tr1knot"
    ) %>%
  pull(parcel) %>%
  unique



## add cols for plotting

coef.means.roi %<>%
  mutate(
    hemi = substr(parcel, 1, 1),
    num.roi = match(parcel, parcellation$key)
    )

```
At FDR-adjusted $\alpha$ = 0.05

* `r length(roi.univ.bas.2tr1knot)` parcels for 2tr1knot, baseline.

`r roi.univ.bas.2tr1knot`

* `r length(roi.univ.bas.1tr1knot)` parcels for 1tr1knot, baseline.

`r roi.univ.bas.1tr1knot`

* `r length(roi.univ.pro.2tr1knot)` parcels for 2tr1knot, proactive.

`r roi.univ.pro.2tr1knot`

* `r length(roi.univ.pro.1tr1knot)` parcels for 1tr1knot, proactive.

`r roi.univ.pro.1tr1knot`



# Brains

* the t statistics from above are plotted on brains here.

## unthresholded

### baseline 1tr1knot

```{r, fig.height = 7, fig.width = 11}

coef.means.roi %>%
  filter(term == "trial.typeInCon", session == "baseline", glm == "1tr1knot") %>%
  build_overlay("statistic", template = schaefer) %>%
  plot_surface(underlay = hcp)

```

### baseline 2tr1knot

```{r, fig.height = 7, fig.width = 11}

coef.means.roi %>%
  filter(term == "trial.typeInCon", session == "baseline", glm == "2tr1knot") %>%
  build_overlay("statistic", template = schaefer) %>%
  plot_surface(underlay = hcp)

```

### proactive 1tr1knot

```{r, fig.height = 7, fig.width = 11}

coef.means.roi %>%
  filter(term == "trial.typeInCon", session == "proactive", glm == "1tr1knot") %>%
  build_overlay("statistic", template = schaefer) %>%
  plot_surface(underlay = hcp)

```

### proactive 2tr1knot

```{r, fig.height = 7, fig.width = 11}

coef.means.roi %>%
  filter(term == "trial.typeInCon", session == "proactive", glm == "2tr1knot") %>%
  build_overlay("statistic", template = schaefer) %>%
  plot_surface(underlay = hcp)

```


## thresholded


### baseline 1tr1knot

```{r, fig.height = 7, fig.width = 11}

coef.means.roi %>%
  filter(term == "trial.typeInCon", session == "baseline", glm == "1tr1knot") %>%
  mutate(statistic = ifelse(p.fdr < 0.05 & statistic > 0, statistic, 0)) %>%
  build_overlay("statistic", template = schaefer) %>%
  plot_surface(underlay = hcp)

```

### baseline 2tr1knot

```{r, fig.height = 7, fig.width = 11}

coef.means.roi %>%
  filter(term == "trial.typeInCon", session == "baseline", glm == "2tr1knot") %>%
  mutate(statistic = ifelse(p.fdr < 0.05 & statistic > 0, statistic, 0)) %>%
  build_overlay("statistic", template = schaefer) %>%
  plot_surface(underlay = hcp)

```

### proactive 1tr1knot

```{r, fig.height = 7, fig.width = 11}

coef.means.roi %>%
  filter(term == "trial.typeInCon", session == "proactive", glm == "1tr1knot") %>%
  mutate(statistic = ifelse(p.fdr < 0.05 & statistic > 0, statistic, 0)) %>%
  build_overlay("statistic", template = schaefer) %>%
  plot_surface(underlay = hcp)

```

### proactive 2tr1knot

```{r, fig.height = 7, fig.width = 11}

coef.means.roi %>%
  filter(term == "trial.typeInCon", session == "proactive", glm == "2tr1knot") %>%
  mutate(statistic = ifelse(p.fdr < 0.05 & statistic > 0, statistic, 0)) %>%
  build_overlay("statistic", template = schaefer) %>%
  plot_surface(underlay = hcp)

```

