---
title: 'UB55 univariate analysis: hi-lo contrast, individual-level'
author: "michael freund"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    highlight: zenburn
    number_sections: true
    theme: spacelab

---


# intro

Purpose: 

1. Assess internal validity (cross-run correlation) of univariate contrast.
2. Assess convergent validity (cross-task correlation) of univariate contrast.


```{r setup, include = FALSE}


source(here::here("code", "_packages.R"))
source(here("code", "read-behav.R"))
source(here("code", "_vars.R"))
source(here("code", "_atlases.R"))
source(here("code", "_settings.R"))
source(here("code", "_funs.R"))

## data ----

glminfo <- data.frame(
  task = c("Axcpt", "Cuedts", "Stern", "Stroop"),
  name.glm = c(
    "baseline_Cues_EVENTS_censored_shifted", 
    "baseline_CongruencySwitch_EVENTS_censored_shifted",
    "baseline_ListLength_EVENTS_censored_shifted",
    "baseline_Congruency_EVENTS_censored_shifted"
  )
)
glminfo <- as.data.table(glminfo)

d <- setNames(vector("list", nrow(glminfo)), glminfo$task)
for (glm.i in seq_len(nrow(glminfo))) {
  # glm.i = 1
  
  a <- readRDS(here("out", "glms", paste0("roistats_", glminfo[glm.i]$task, "_", glminfo[glm.i]$name.glm, ".RDS")))
  a <- a[, , subjs[!subjs %in% "432332"], ]
  a <- as.data.table(reshape2::melt(a))
  
  a <- separate(a, term, c("term", "stat"), "_")
  a <- a[!grepl("Full|block", term) & stat == "Coef"]
  a <- separate(a, term, c("term", "tr"), "#")
  
  a$network <- a$parcel %>% gsub("LH_|RH_", "", .) %>% gsub("_.*", "", .)
  a$hemi <- substr(a$parcel, 1, 1)
  
  if (!identical(unique(a$stat), "Coef")) stop("more stats than coef in there")
  # a <- dcast(a, term + tr + parcel + subj + run + hemi + network ~ stat, value.var = "value")
  # names(a) <- tolower(names(a))
  
  a$stat <- NULL
  a <- rename(a, b = value)
  
  d[[glm.i]] <- a
  
}
rm(glm.i, a)
gc()

## fix cuedts labels: incorrect! (mislabeled in afni code)
d$Cuedts$term <- gsub("NoInc$", "Repeat", d$Cuedts$term)
d$Cuedts$term <- gsub("Inc$", "Switch", d$Cuedts$term)


## bind and create data.tables suitable for looping

d <- bind_rows(d, .id = "task")
d.marginal <- d[, .(b = mean(b)), by = .(task, run, network, parcel, tr, subj)]  ## average across conditions
d.contrast <- rbind(
  
  d[task == "Axcpt" & term %in% c("BX", "BY"), ] %>%
    dcast(... ~ term, value.var = "b") %>%
    mutate(b = BX - BY) %>% select(-BX, -BY),
  
  d[task == "Cuedts"] %>% 
    dcast(... ~ term, value.var = "b") %>%
    mutate(b = (InConSwitch + InConRepeat - ConSwitch - ConRepeat)/2, tr = as.numeric(tr)) %>% 
    select(-InConSwitch, -InConRepeat, -ConSwitch, -ConRepeat),
  
  d[task == "Stern" & term %in% c("LL5RN", "LL5NN")] %>%
    dcast(... ~ term, value.var = "b") %>%
    mutate(b = LL5RN - LL5NN, tr = as.numeric(tr)) %>%
    select(-LL5NN, -LL5RN),
  
  d[task == "Stroop"] %>%
    dcast(... ~ term, value.var = "b") %>%  
    mutate(b = (biasInCon + PC50InCon - biasCon - PC50Con)/2, tr = as.numeric(tr)) %>%
    select(-biasInCon, -PC50InCon, -biasCon, -PC50Con)

)


group.target.trs <- fread(here("out", "stats_univ_hilo_target_schaefer400-07.csv"))
dmcc55b.parcels <- group.target.trs %>% filter(estimate > 0, p.fdr < 0.05) %>% pull(parcel) %>% table
dmcc55b.parcels <- names(dmcc55b.parcels)[dmcc55b.parcels == 4]


w.contrast <- d.contrast %>% dcast(... ~ run, value.var = "b")



```







# cross-run correlations

### Network-level curves

```{r crossrun_network, fig.width = 8, fig.height = 10}

d.contrast %>%
  
  dcast(... ~ run, value.var = "b") %>%
  
  group_by(task, network, tr) %>%
  summarize(
    r = cor(run1, run2), 
    rho = cor(run1, run2, method = "spearman"), 
    .groups = "drop_last"
    ) %>%
  
  as.data.table %>%
  melt(id.vars = c("task", "network", "tr"), measure.vars = c("r", "rho")) %>%

  ggplot(aes(as.numeric(tr), value)) +
  geom_hline(yintercept = 0) +
  geom_line(aes(color = variable), size = 2) +

  facet_grid(vars(network), vars(task), scales = "free_x") +
  scale_x_continuous(breaks = seq(0, 20, 4)) +
  
  scale_color_brewer(type = "qual", palette = 3, name = NULL, labels = c("r" = "linear corr", "rho" = "rank corr")) +
  theme(legend.position = "top") +
  
  labs(
    y = "cross-run correlation", 
    x = "TR post stimtime", 
    title = "split-half (cross-run) reliability in HiLo contrast"
  )


```

### Parcel-level curves (DMCC55B univariate ROIs)

```{r crossrun_dmcc55b, fig.width = 15, fig.height = 12}


for (task.i in tasks) {
  
 
  p.crossrun <- d.contrast %>%
    
    filter(task %in% task.i, parcel %in% dmcc55b.parcels) %>%
    
    dcast(... ~ run, value.var = "b") %>%
    
    group_by(task, parcel, tr) %>%
    summarize(
      r = cor(run1, run2), 
      rho = cor(run1, run2, method = "spearman"), 
      .groups = "drop_last"
      ) %>%
    
    as.data.table %>%
    melt(id.vars = c("task", "parcel", "tr"), measure.vars = c("r", "rho")) %>%
  
    ggplot(aes(as.numeric(tr), value)) +
    geom_hline(yintercept = 0) +
    geom_line(aes(color = variable), size = 2) +
  
    facet_wrap(vars(parcel)) +
    scale_x_continuous(breaks = seq(0, 20, 4)) +
    
    scale_color_brewer(type = "qual", palette = 3, name = NULL, labels = c("r" = "linear corr", "rho" = "rank corr")) +
    theme(legend.position = "top") +
    
    labs(
      y = "cross-run correlation", 
      x = "TR post stimtime", 
      title = paste0(task.i, ": split-half (cross-run) reliability in HiLo contrast")
    )
 
  print(p.crossrun)
  
}

```



## Target TRs: Parcel-level scatterplots (DMCC55B univariate ROIs)

```{r crossrun_dmcc55b_scatter, fig.width = 8, fig.height = 10}




for (task.i in tasks) {
  
 
  p.scatter <- d.contrast %>%
    
    filter(task %in% task.i, parcel %in% dmcc55b.parcels, tr %in% target.trs[[task.i]]) %>%
    
    group_by(task, network, parcel, subj, run) %>%
    summarize(
      b = mean(b),
      .groups = "drop_last"
      ) %>%

    as.data.table %>%
    dcast(... ~ run, value.var = "b") %>%
    
    ggplot(aes(run1, run2)) +
    geom_hline(yintercept = 0) +
    geom_vline(xintercept = 0) +
    geom_point(aes(fill = network), color = "white", size = 2, shape = 21) +
  
    facet_wrap(vars(parcel)) +
    
    scale_fill_brewer(type = "qual", palette = 2) +
    theme(legend.position = "top") +
    
    labs(
      y = "run 2 beta contrast", 
      x = "run 1 beta contrast", 
      title = paste0(task.i, ": HiLo contrast at target TRs")
    )
 
  print(p.scatter)
  
}





```





# cross-parcel correlations

## DMCC55B ROIs (univariate)

```{r crossparcel_dmcc55b, fig.width = 6, fig.height = 6.5, results = "asis"}



for (task.i in tasks) {
  
  cat("\n ")
  cat(sprintf("\n### %s ", task.i))
  cat("\n ")

  
  R.dmcc55b <- d.contrast %>% 
    
    .[task.i == task & tr %in% target.trs[[task.i]] & parcel %in% dmcc55b.parcels, 
      .(b = mean(b)), 
      by = c("task", "parcel", "subj")] %>%
    
    dcast(... ~ parcel, value.var = "b") %>%
    select(where(is.numeric)) %>%
    
    cor
  
  p.R.dmcc55b <- R.dmcc55b %>%
    
    symmat4ggplot %>%
    
    ggplot(aes(v1, v2, fill = value)) +
    geom_raster() +
    
    scale_fill_viridis_c(option = "magma", name = NULL) +
    
    theme_minimal() +
    theme(
      axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1),
      axis.title = element_blank(), 
      title = element_text(size = rel(1.5)),
      legend.position = "top", panel.border = element_blank(), panel.grid = element_blank()
      )
  
  print(p.R.dmcc55b)
  cat("\n ")
  
  
  pca.dmcc55b <- prcomp(R.dmcc55b, scale = TRUE)
  subchunkify(plot(pca.dmcc55b, main = NULL), fig_height = 4, fig_width = 6)
  
  
  p.pca.dmcc55b <- pca.dmcc55b$rotation[, 1:2] %>%
    
    as.data.frame %>%
    tibble::rownames_to_column("parcel") %>%
    mutate(network = get.network(parcel)) %>%
    
    ggplot(aes(PC1, PC2, color = network)) +
    
    geom_point(size = 2) +
    geom_text(aes(label = parcel), fontface = "bold", nudge_y = -0.01) +
    scale_color_brewer(type = "qual", palette = 2) +
    
    theme(legend.position = "none")
  
  subchunkify(p.pca.dmcc55b, fig_height = 6, fig_width = 6)

  
}



```










# cross-task correlations


## Per parcel



```{r fig.width = 10, fig.height = 10}

d.contrast$is.target <- FALSE
for (task.i in tasks) d.contrast[task.i == task & tr %in% target.trs[[task.i]]]$is.target <- TRUE

d.contrast.target <- d.contrast[is.target == TRUE, .(b = mean(b)), by = c("task", "subj", "parcel")]
R.task.per.parcel <- enlist(dmcc55b.parcels)
for (parcel.i in dmcc55b.parcels) {
  
  R.task.per.parcel[[parcel.i]] <- 
    
    d.contrast.target[parcel == parcel.i] %>%
    dcast(... ~ task, value.var = "b") %>%
    select(where(is.numeric)) %>%
    cor

}

d.task.per.parcel <- bind_rows(lapply(R.task.per.parcel, symmat4ggplot), .id = "parcel")

d.task.per.parcel %>%
  
  ggplot(aes(v1, v2, fill = value)) +
  geom_raster() +
  geom_text(aes(label = round(value, 1))) +
  
  scale_fill_viridis_c(option = "magma", name = NULL) +
  
  facet_wrap(vars(parcel)) +
  
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1),
    axis.title = element_blank(), 
    title = element_text(size = rel(1.5)),
    legend.position = c(0.92, 0.05), 
    # legend.direction = "horizontal",
    panel.border = element_blank(), panel.grid = element_blank()
    ) +
  
  labs(title = "cross-task correlations in subjects' effect size per DMCC55B ROI")
  
stats.task.per.parcel <- data.frame(
  parcel = names(R.task.per.parcel),
  invdet = 1 / vapply(R.task.per.parcel, det, numeric(1)),
  mean_offdiag = vapply(R.task.per.parcel, function(x) mean(atanh(x[lower.tri(x)])), numeric(1))
)


```


```{r fig.width = 4, fig.height = 6}


stats.task.per.parcel %>%
  
  ggplot(aes(invdet, parcel, color = get.network(parcel))) +
  geom_point() +
  geom_segment(aes(x = 0, xend = invdet, y = parcel, yend = parcel)) +
  theme(legend.position = "none")

stats.task.per.parcel %>%
  
  ggplot(aes(mean_offdiag, parcel, color = get.network(parcel))) +
  geom_point() +
  geom_segment(aes(x = 0, xend = mean_offdiag, y = parcel, yend = parcel)) +
  theme(legend.position = "none")


```






## Multi-parcel


* reduce subj to single number per task
  * align PCs
  * within vs btw network contrast
  * ...






