---
title: 'UB55 multivariate analysis: hi-lo contrast, group-level'
author: "michael freund"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    highlight: zenburn
    number_sections: true
    theme: spacelab
---


# intro

Purpose: 

1. Preliminary look at hi/lo multivariate contrast (cross-validated euclidean) in each task.
2. Preliminary qualitative comparison of effects of prewhitening and pattern standardization on multivariate contrast.
    


```{r setup, include = FALSE}

source(here::here("code", "_packages.R"))
source(here("code", "read-behav.R"))
source(here("code", "_vars.R"))
source(here("code", "_atlases.R"))
source(here("code", "_settings.R"))
source(here("code", "_funs.R"))

## data ----

glminfo <- data.frame(
  task = c("Axcpt", "Cuedts", "Stern", "Stroop"),
  name.glm = c(
    "baseline_Cues_EVENTS_censored_shifted", 
    "baseline_CongruencySwitch_EVENTS_censored_shifted",
    "baseline_ListLength_EVENTS_censored_shifted",
    "baseline_Congruency_EVENTS_censored_shifted"
  )
)
glminfo <- as.data.table(glminfo)

weights_hi <- list(
  Axcpt  = c(AX = 0, AY = 0, Ang = 0, BX = 1, BY = 0, Bng = 0),
  Cuedts = c(ConInc = 0, ConNoInc = 0, InConInc = 1, InConNoInc = 1) / 2,
  Stern  = c(LL5NP = 0, LL5NN = 0, LL5RN = 1, not5NP = 0, not5NN = 0, not5RN = 0),
  Stroop = c(PC50Con = 0, PC50InCon = 1, biasCon = 0, PC50InCon = 1) / 2
)

weights_lo <- list(
  Axcpt  = c(AX = 0, AY = 0, Ang = 0, BX = 0, BY = 1, Bng = 0),
  Cuedts = c(ConInc = 1, ConNoInc = 1, InConInc = 0, InConNoInc = 0) / 2,
  Stern  = c(LL5NP = 0, LL5NN = 1, LL5RN = 0, not5NP = 0, not5NN = 0, not5RN = 0),
  Stroop = c(PC50Con = 1, PC50InCon = 0, biasCon = 1, biasInCon = 0) / 2
)



similtype <- c(
  "euclidean-cv-unsta-prewh", "euclidean-cv-stand-prewh", "euclidean-cv-unsta-unpre", "euclidean-cv-stand-unpre"
  )

d <- setNames(vector("list", nrow(glminfo)), glminfo$task)
for (rsa.i in similtype) {
  # rsa.i = similtype[1]
  
  l <- setNames(vector("list", nrow(glminfo)), glminfo$task)
  for (glm.i in seq_len(nrow(glminfo))) {
    # glm.i = 4
    
    a <- readRDS(here("out", "rsa", paste0(rsa.i, "_", glminfo[glm.i]$task, "_", glminfo[glm.i]$name.glm, ".RDS")))
    
    ## standardize each RDM by the sd of unique off-diagonals:
    sds <- apply(a, c("tr", "parcel", "subj"), function(x) sd(x[lower.tri(x)]))
    a <- sweep(a, MARGIN = 3:5, STATS = sds, FUN = "/")
    
    ## apply contrast:
    a <- apply(a, c("tr", "parcel", "subj"), function(x) weights_lo[[glm.i]] %*% x %*% weights_hi[[glm.i]])
    a <- as.data.table(reshape2::melt(a))
    
    a$network <- a$parcel %>% gsub("LH_|RH_", "", .) %>% gsub("_.*", "", .)
    a$hemi <- substr(a$parcel, 1, 1)
    
    l[[glm.i]] <- a
    
  }
  
  d[[rsa.i]] <- bind_rows(l, .id = "task")
  
}

d <- as.data.table(bind_rows(d, .id = "similtype"))
d <- d[subj != "448347"]


facet_labels <- c(
  "euclidean-cv-stand-prewh" = "stand white",
  "euclidean-cv-stand-unpre" = "stand unwhite",
  "euclidean-cv-unsta-prewh" = "unstand white",
  "euclidean-cv-unsta-unpre" = "unstand unwhite" 
)


```



Notes on analyses:

Target TRs:

  * Axcpt: `r target.trs$Axcpt`
  * Cuedts: `r target.trs$Cuedts`
  * Stern: `r target.trs$Stern`
  * Stroop: `r target.trs$Stroop`

Contrasts (cross-validated euclidean):

  * Axcpt: $\text{BY} - \text{BX}$
  * Cuedts: $(\text{InConSwitch} + \text{InConRepeat} - \text{ConSwitch} - \text{ConRepeat})/2$
  * Stern: $\text{LL5RN} - \text{LL5NN}$
  * Stroop: $(\text{PC50InCon} + \text{biasInCon} - \text{PC50Con} - \text{biasCon})/2$

Normalizations:

  * "stand": standardized cross-validated euclidean (comparable to linear correlation)
  * "unsta": unstandardized cross-validated euclidean (includes mean and scale information)
  * "white": spatially pre-whitened cross-validated euclidean ('mahalanobis')
  * "unwhite": not spatially pre-whitened

Plotting and statistical details:

  * within 'curves' sections, ribbons indicate 95% CI of bootstrapped mean beta across subjects (one ribbon per run).
  * all p-value corrections were performed whole-cortex, with FDR.
  * for "stats and maps" sections, HLM was used to estimate t-statistics on the hi-lo contrast per ROI:
      * random-intercept models
      * level-I: (TR within target window)\*(run)
      * level-2: subject
      * $\beta_{trs} = b_0 + x_{tr}b_1 + d_s + \epsilon_{trs}$
        * $t, r, s$ are indices for TR, run, and subject
        * $x$ is dummy-coded predictor for hi condition; $b_1$ reflects hi-lo contrast (fixed effect)
        * $d$ is is subject-specific intercept
        * $\epsilon$ is error



# Network-level

Estimates are first averaged across parcels within network per subject.
Group-level stats and plots are then displayed at the network-level.

## curves

### beta contrasts

```{r network_curves_b, fig.height = 7}

d.network.curves <- d[, .(m = mean(value)), by = .(similtype, task, network, tr, subj)]

for (task.i in tasks) {
  
  p.network.curves  <- d.network.curves %>%
    
    filter(task == task.i) %>%
    mutate(tr = as.numeric(tr)) %>%
    
    ggplot(aes(tr, m)) +
    geom_hline(yintercept = 0) +
    geom_boxplot(width = 0.5, aes(group = tr)) +
    stat_summary(fun.data = "mean_cl_boot", geom = "ribbon", alpha = 1/2) +
    
    facet_grid(
      vars(similtype), vars(network), 
      scale = "free_y", 
      labeller = labeller(similtype = facet_labels)
      ) +
    scale_x_continuous(breaks = seq(0, 20, 4)) +
    scale_fill_brewer(type = "qual", palette = 2)  +
    
    labs(y = "Mean contrast (beta)", x = "TR post stimtime", title = task.i)
  
  print(p.network.curves)
  
}

```


### t-stats on contrast

```{r network_curves_t, fig.height = 7}

d.network.curves.group <- d.network.curves %>%

  group_by(task, tr, network, similtype) %>%
  summarize(
    p = t.test(m)$p.value,
    t = t.test(m)$statistic,
    b = mean(m)
  ) %>%

  group_by(task, tr, similtype) %>%
  mutate(p.fdr = p.adjust(p, "fdr"))


for (task.i in tasks) {
  
  p.network.curves.group <- d.network.curves.group %>%
  
    filter(task == task.i) %>%
  
    mutate(tr = as.numeric(tr)) %>%
  
    ggplot(aes(tr, t, color = similtype, group = similtype)) +
    geom_hline(yintercept = 2, color = "grey50", linetype = "dashed") +
    geom_hline(yintercept = -2, color = "grey50", linetype = "dashed") +
    geom_hline(yintercept = 0) +
  
    geom_line(size = 2) +
  
    facet_wrap(vars(network)) +
    scale_color_brewer(type = "qual", palette = 2, labels = facet_labels) +
    scale_x_continuous(breaks = seq(0, 20, 4)) +
    
    theme(legend.position = c(0.5, 0.15)) +
  
    labs(y = "t statistic on contrast", x = "TR post stimtime", title = task.i)
  
  p.network.curves.group
  
}

```


# parcel-level

```{r}

d.parcel.curves.group <- d %>% 
  .[, 
    .(b = mean(value), t = t.test(value)$statistic, p = t.test(value)$p.value), 
    by = .(similtype, task, parcel, tr)
    ] %>%
  group_by(task, tr, similtype) %>% 
  mutate(p.fdr = p.adjust(p, "fdr"))

```



## curves

```{r}

counts.parcel.curves.group <- d.parcel.curves.group %>%
  
  group_by(task, similtype, tr) %>%
  summarize(
    nparc.activ = sum(b > 0 & p.fdr < 0.05),
    nparc.deactiv = -sum(b < 0 & p.fdr < 0.05)
    ) %>%
  reshape2::melt(id.var = c("task", "tr", "similtype"))


```


### counts of significant effects per TR

```{r, fig.height = 7}
  
counts.parcel.curves.group %>%
  
  ggplot(aes(as.numeric(tr), value, color = variable)) +
  geom_hline(yintercept = 0) +
  geom_point(size = 2) +
  geom_segment(aes(xend = tr, yend = 0), size = 1) +
  
  facet_grid(vars(similtype), vars(task), labeller = labeller(similtype = facet_labels)) +
  scale_color_brewer(type = "qual", palette = 1) +
  scale_x_continuous(breaks = seq(0, 20, 2)) +
  theme(legend.position = "none") +
  
  labs(
    y = "N parc w/ sig. hilo contrast (FDR corrected whole-cortex)", 
    x = "TR post stimtime", title = "counts of contrast where pFDR < 0.05"
    )

```



### runwise univariate ROIs

```{r, fig.height = 7}

parcels.univ.conj <- fread(here("out", "conjunction_univ_hilo_target_schaefer400-07.txt"))[[1]]


for (task.i in tasks) {
  
  p.parcel.curves  <- d.parcel.curves.group %>%
    
    filter(task == task.i, parcel %in% parcels.univ.conj) %>%
    mutate(tr = as.numeric(tr)) %>%
    
    ggplot(aes(tr, t, color = similtype, group = similtype)) +
    geom_hline(yintercept = 2, color = "grey50", linetype = "dashed") +
    geom_hline(yintercept = -2, color = "grey50", linetype = "dashed") +
    geom_hline(yintercept = 0) +
  
    geom_line(size = 2) +
  
    facet_wrap(vars(parcel)) +
    scale_color_brewer(type = "qual", palette = 2, labels = facet_labels) +
    scale_x_continuous(breaks = seq(0, 20, 4)) +
    
    theme(legend.position = "top") +
  
    labs(y = "t statistic", x = "TR post stimtime", title = paste0(task.i, ", parcels in univariate hilo conjunction"))
  
  print(p.parcel.curves)
  
}


```


### largest 20 ROIs


```{r, fig.height = 7}

parcels.univ.conj <- fread(here("out", "conjunction_univ_hilo_target_schaefer400-07.txt"))[[1]]


for (task.i in tasks) {
  
  parcels.max20 <- d.parcel.curves.group %>% 
          filter(task == task.i) %>%
          ungroup %>%
          slice_max(order = abs(t), n = 20) %>% pull(parcel) %>% unique
  
  p.parcel.curves  <- d.parcel.curves.group %>% 
    
    filter(task %in% task.i, parcel %in% parcels.max20) %>%
    
    mutate(tr = as.numeric(tr)) %>%
    
    ggplot(aes(tr, t, color = similtype, group = similtype)) +
    geom_hline(yintercept = 2, color = "grey50", linetype = "dashed") +
    geom_hline(yintercept = -2, color = "grey50", linetype = "dashed") +
    geom_hline(yintercept = 0) +
  
    geom_line(size = 2) +
  
    facet_wrap(vars(parcel)) +
    scale_color_brewer(type = "qual", palette = 2, labels = facet_labels) +
    scale_x_continuous(breaks = seq(0, 20, 4)) +
    
    theme(legend.position = "top") +
  
    labs(y = "t statistic", x = "TR post stimtime", title = paste0(task.i, ", 20 parcels with maximum abs(t) stats"))
  
  print(p.parcel.curves)
  
}


```





## maps (target TRs)


```{r stats}


# d.group <- enlist(tasks)
# for (task.i in tasks) {
#   
#   
#   d.i <- d[task %in% task.i & tr %in% target.trs[[task.i]]]
#   
#   
#   l <- split(d.i, interaction(d.i$parcel, d.i$similtype))
#   m <- lapply(l, function(x) lmer(value ~ 1 + (1 | subj), x))
#   s <- bind_rows(lapply(m, tidy_lmer), .id = "parcel.similtype")
#   s <- cbind(s, reshape2::colsplit(s$parcel.similtype, "\\.", c("parcel", "similtype")))
#   s %<>% 
#     mutate(
#       parcel.similtype = NULL,
#       term = NULL,
#       p.fdr = p.adjust(p.value, "fdr"), 
#       network = get.network(parcel),
#       hemi = substr(parcel, 1, 1),
#       num.roi = match(parcel, parcellation$key)
#       )
#   
#   
#   d.group[[task.i]] <- s
#   
#   
# }
# 
# 
# lapply(d.group, function(x) filter(x, p.fdr < 0.05 & estimate > 0) %>% nrow)
# 
# 
# d.group <- bind_rows(d.group, .id = "task")
# 
# 
# fwrite(d.group, here("out", "stats_multiv-euclidean-cv_hilo_target_alltasks_schaefer400-07.csv"))

d.group <- fread(here("out", "stats_multiv-euclidean-cv_hilo_target_alltasks_schaefer400-07.csv"))

```


Unthresholded and thresholded t-statistics displayed on inflated brains.
Threshold at fdr-corrected p-value (across all parcels) of 0.05.
Note: colors are reverse-scaled, i.e., dark == strong effect, light == weak effect (so strong effects show up on white background).

```{r maps_hilo, fig.height = 7, fig.width = 11, results = "asis"}


for (task.i in tasks) {
  
  cat(sprintf("\n### %s", task.i))
  
  for (similtype.i in similtype) {
    
    
    cat(sprintf("\n#### %s", facet_labels[similtype.i == names(facet_labels)]))
    
    
    d.group %>%
      
      filter(task == task.i, similtype == similtype.i) %>%
      
      build_overlay("statistic", template = schaefer) %>%
      plot_surface(underlay = hcp.vinf, hues = rev(viridis::inferno(500)))
    
    
    d.group %>%
      
      filter(task == task.i, similtype == similtype.i) %>%
      mutate(statistic = ifelse(p.fdr < 0.05, statistic, 0)) %>%
      
      build_overlay("statistic", template = schaefer) %>%
      plot_surface(underlay = hcp.vinf, hues = rev(viridis::inferno(500)))

    
  }
}


```


